\Large{Adversarial Training against Systematic Uncertainty}

### 2016-09-29 tex/paper.tex
first draft of abstract (#6)
* first draft of abstract

* now updating pdf after merge

\begin{abstract}

Nice and cozy abstract goes here...

>>>>

\begin{abstract}
Systematic uncertainties in high energy physics, representing
incomplete knowledge in the simulation of physical processes or
detection appartus, may cause variations in the class conditional
distributions of features used for training a classifier.  As such,
the efficiacy of a classifier may change under the variations caused
by systematic uncertainties.  In this paper, we propose an adversarial
training procedure to produce a pivotal
classifier which is invariant to variations of nuisance parameters
which parameterize the effects of systematic uncertainties.
In the machine learning context, this problem is closely related to those of domain
adaptation and enforcing fairness in classification.  The techniques
described here can handle the case of continuous nuisance paramater
variations that represents domain adaptation over infinitely many domains.
